Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-03 Draft/Draft.Rmd
playing with colors

ggplot(NULL) + 
  geom_point(data = d %>% filter(motif != 1),
             aes(y=as.factor(motif), x=percentil_sizeclass, 
                 color = as.factor(Broad_categories)),
             position = "jitter",alpha=0.55)+
  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=mean-SE, xmax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = motif_means,aes(y = as.factor(motif), x=mean), 
                size=2)+
  labs(y="Motif", x = "Percentile",colour="Path length classification")+
  theme_bw() + scale_color_manual(labels = c('Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")),
    'Strong' = expression(paste("Complete (", bar(x), " = 1.38)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("deepskyblue3","maroon","darkgoldenrod2","grey25")) +
theme(legend.text.align = 0)

>>>>

#order the categories from short to long path length
d$Broad_categories <- factor(d$Broad_categories, levels = c("Strong", "Fan", "Medium-weak", "Weak"))

ggplot(NULL) + 
  geom_point(data = d %>% filter(motif != 1),
             aes(y=as.factor(motif), x=percentil_sizeclass, 
                 color = as.factor(Broad_categories)),
             position = "jitter",alpha=0.5)+
  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=mean-SE, xmax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = motif_means,aes(y = as.factor(motif), x=mean), 
                size=2)+
  labs(y="Motif", x = "Percentile",colour="Path length classification")+
  theme_bw() + scale_color_manual(labels = c('Strong' = expression(paste("Complete (", bar(x), " = 1.38)")),'Fan' = expression(paste("Fan (", bar(x), " = 1.48)")), 'Medium-weak' = expression(paste("Asymmetric complete (", bar(x), " = 1.60)")), "Weak" =expression(paste("Core-peripheral (", bar(x), " = 1.85)"))), name = "Path length classification",values = c("grey25","springgreen4","sienna2","goldenrod2")) +
theme(legend.text.align = 0)

#Trying to maintain a gradient from low to high in colors
